---
title: "A minimal example"
date: today
author: First Last 
format: html # revealjs is for slides
execute:
  warning: false # don't show any warnings in the output
  # echo: false # this removes the code that produces figures 
editor: visual
editor_options: 
  chunk_output_type: console
---

## Data

For this analysis we'll use the penguins dataset from the palmerpenguins R package.

```{r}
#| label: load-packages

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```

## Species

@fig-penguins is a scatterplot of species of penguins.

```{r}
#| fig-cap: Bill length and depth of penguins
#| label: fig-penguins

ggplot(data = penguins,
       mapping = aes(x = bill_length_mm, 
                     y = bill_depth_mm,
                     color = species,
                     shape = species)) +
  geom_point() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)") +
  theme_minimal()
```

## Penguins

-   for cross references, you must have 3 things:

    -   a label, that starts with "fig"or "tbl" depending on if its a figure or table

    -   needs a caption with "tbl-cap" or "fig-cap"

    -   reference with an `@fig-label`

@tbl-penguins shows a summary of for the bill depth of penguins by island and species.

```{r}
#| label: tbl-penguins
#| tbl-cap: Bill depth of penquins by island and species.

penguins |> 
  filter(!is.na(bill_depth_mm)) |> 
  group_by(island, species) |>
  summarise(n = n(),
            mean_bill_depth = mean(bill_depth_mm),
            sd_bill_depth = sd(bill_depth_mm)) |>
  ungroup() |> 
  gt() |> 
  fmt_number(columns = c(mean_bill_depth, sd_bill_depth),
             decimals = 1)
```
